\section{Broader Impacts}

\paragraph{Improving Software System Reliability:} A key element of
our approach is to focus on realistically deployable techniques.  We aim
for early integration with NASA's FPrime~\cite{fprime,fprimerepo}
open source
flight software architecture and platform; PI Groce is already in
discussion with engineers at NASA's Jet Propulsion Laboratory, and
engaged in producing tests for the FPrime autocoder using DeepState.
This integration will allow our
methods to be applied to CubeSat missions (and other flight software
systems), leading to improved reliability for low-budget space-based
scientific efforts.  We expect, in the long run, that our approaches
will lead to more reliable and robust development in many embedded and
cyberphysical systems domains.  Our engagement with interested Galois
engineers ensures the applicability of our methods will be as wide as
possible, and impact tools outside our initial scope.

\paragraph{Education and Outreach:}
The proposed research yields several opportunities for enhancing CS
education, recruiting new CS majors, and retaining CS students,
particularly members of underrepresented groups.  In addition to the
activities discussed at length in the Broadening Participation in
Computing plan, PI Groce will work with the NAU Student ACM Chapter to
present a series of ``excursions in testing'' that introduce automated
testing to students, using DeepState to find bugs in real world code,
including code from media player libraries.  The
work of Guzdial \cite{Guzdial} has shown that media computation is an effective way to both recruit and retain female and
underrepresented students in computer science. Groce is also teaching
a class on automated testing of embedded systems.  Co-PI Nghiem has
developed a course on  autonomous vehicles, based on the F1/10 platform (funded by
NSF). 
To prepare students for addressing safety in autonomous driving, future offerings of the course will incorporate the methods and tools developed in this project.
%Each year, Loulergue teaches CS451/551 Mechanized Reasoning about Programs to about 40 students.
%This class is based on \framac, and Loulergue transitions his research on formal methods into this class.
%Loulergue has presented many \framac tutorials in conference such as ISSRE, ACM SAC, FM, SecDev, {\it etc.}, and will continue to do so.


\paragraph{Broadening Participation in Computing (BPC):}
\input{bpc}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
