%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt]{article}

\usepackage{fullpage}
\input{packages}
\input{commands}

\begin{document}

\pagenumbering{gobble}

\begin{center}
{\large\sf\bfseries FMiTF: Track l: Combining Formal, Static, and
  Dynamic Analysis to Verify and Validate Real-World Embedded Systems: Collaboration Plan}
\end{center}

\section{PI Qualifications}

PI Groce has a long history with formal methods, including involvement in design and development of well-known model checkers, and application of model checkers at NASA/JPL on flight software for the Mars rovers, including application of and development contributions to, the SPIN and CBMC model checkers.  Groce was the lead for design and development of automated testing tools and specification languages for the Mars Science Laboratory (Curiosity Rover) project.  He received his PhD under the late Turing laureate Edmund M. Clarke, Jr., as one of the first PhD graduates focusing on model checking for software using SAT and SMT solvers.  More recently, he has primarily focused on developing algorithms and tools for automated software testing; he is a core member of the DeepState and TSTL design and development teams.  Groce is the lead developer for multiple GitHub-hosted testing and verification tools (including DeepState, the focus platform for this project), all with more than 100 GitHub ``stars''; he reports 50-100 bugs detected using such tools to open source projects each year, and has been awarded significant bug bounties for security-critical compiler bugs detected using his work.  Groce was recently chosen by the Bitcoin Core team to investigate the effectiveness of their fuzzing framework.
%Co-PI Loulergue has a long experience in designing parallel programming languages and libraries based on formal semantics. About ten years ago, he started using the \Coq proof assistant in his research on programming language semantics and on the development of parallel programs correct by construction. More recently he has begun a collaboration with colleagues at {\it Commissariat \`a l'\'energie atomique et aux \'energies alternatives} (CEA), extending \framac with new features, motivated by analysis and verification tasks on real-world code. He brings to this project a strong expertise in static analysis and deductive verification of C programs with the \framac framework, and on specification and proof engineering on real-world code. 

Co-PI Nghiem has an extensive background in control and autonomous systems, including terrestrial rovers and unmanned aerial vehicles (UAVs), and application of formal methods in control systems.
He has long experience working with timed automata and the Uppaal tool family.
He developed, and was granted a U.S. patent for, methods for testing and verifying temporal logic specifications of hybrid systems---systems with both continuous and discrete behaviors.
He brings to this project advanced knowledge of real-time embedded systems and practical experience applying verification methods and tools to them.
He will also
apply our methods and approaches to a multi-agent robotics system.


\section{Collaboration Plan}

The PIs are all faculty in the School of Informatics, Computing and Cyber Systems at Northern Arizona University.  They all work in the same building, which also hosts the DISCOVER lab.  The PIs have toured each others' labs and reviewed code developed by the other PIs.  PIs will meet weekly for technical discussion and project status updates, depending on project status (and already do so, in discussions of the preliminary work) to coordinate their efforts, and ensure that tasks in the work plan are proceeding correctly, and to receive feedback on current status of tools.  These meetings will alternate between meetings with just PIs, focused on higher level decision-making, and full meetings focusing on status of individual work packages.
%In addition to weekly project meetings, there will be special out-of-band meetings to demonstrate significant new functionalities in tools, or to focus particularly on application of functionalities to specific DISCOVER components.

The DISCOVER code forms a core concern that helps focus PI interactions, and enables easier communication of technical results between static and dynamic analysis experts and experts in the embedded systems domain.  PIs will also set up a project repository, separate from DeepState or DISCOVER code repositories (already in existence) and use PR, tagged Issues, and other GitHub-supported collaborative software development best practices to ensure documentation of development, and team awareness of code status for components.  GitHub Actions-based will be used to ensure all project members are aware of build or correctness problems with project code.  All project members will also share a Project Slack Instance to facilitate archived, asynchronous discussion of project issues.
PI Groce is well experienced in coordination of complex research efforts focused on open-source tools, as he coordinates efforts for the DeepState project, which has 16 contributors, and has managed releases of the echidna smart contract fuzzer (both tools with more than 700 GitHub stars and with dozens of forks; echidna has more than 20 contributors).

%\subsection{Work Plan and Evaluation Measures}
\label{sec:workplan}
\input{workplan}

%\subsection{Risks and Mitigations}

%Based on the project goals, we view the primary risk as loss of focus on a coherent application to the case study problems.  This project is to be driven by embedded systems engineering needs, since we view advances that enable real-world usability and cost effectiveness as they key missing features in the application of formal methods to embedded systems engineering.  

%The second primary risk addressed by the plan is that while many research efforts do not require production-quality software, we aim to primarily operate through enhancements to existing, production-quality, tools.  As noted, we will be applying a more rigorous development process than is frequently used in academic software systems.  Because advances in formal methods application to real software are frequently rooted in heuristic solutions (since the general problem is usually infeasible, due to, e.g., Rice's theorem), correct and robust tool implementation work is essential to proper evaluation of advances.
\end{document}
