 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt]{article}

\usepackage{fullpage}

\begin{document}

\pagenumbering{gobble}

\begin{center}
  {\large\sf\textbf{FMiTF: Track l: Combining Formal, Static, and
  Dynamic Analysis to Verify and Validate Real-World Embedded Systems: Data Management Plan}}
\end{center}

The data in the proposed project is primarily either source code for
the tools developed to implement the algorithms and ideas involved or
actual models and annotated code associated with the case study.  The source code will be released either in a project GitHub repository to be created, or incorporated into existing open source projects (e.g., DeepState and CBMC).  Models and annotations will be released to DISCOVER-related GitHub repositories.  In general, this project relies on already open source systems, and exists primarily to extend those systems.  Any experimental data should be reproducible using the code artifacts, but will also be published in a condensed form in the repositories.

Curricular
materials and documentation associated with any tools will also be stored in
an open source repository, since in this project the primary
educational benefits are linked to the use these tools.  Using GitHub automatically provides us with excellent backup
and archiving for the code and curricular material products of the
project.

We have no unusual format or metadata requirements; the
tools involved use textual formats that are easy to store and read;
primarily, in fact, they use textual source code.  DeepState additionally stores tests in a raw binary format; however, DeepState's essential purpose is to parse this format into a test case semantics, so no additional effort is needed to handle the problem.  
We do not anticipate the need to work with sensitive or confidential
information; no extraordinary practices are required in order to
conduct this research.

\end{document}
