\section{Results From Prior NSF Support}

\paragraph{PI Groce:}
The most relevant prior NSF support for PI Groce is CCF-
CCF-2129446, ``Feedback-Driven Mutation Testing for Any Language,'' with a total budget of \$500,000 from 9/2021 until 8/2024,
a collaborative proposal with Claire Le Goues of Carnegie Mellon
University. {\bf Intellectual Merit:} This project
focuses on a synergistic approach for allowing developers
to improve testing by using mutation testing to identify
weaknesses in tests and to generate tests.  This project has resulted in six
publications~\cite{cc2022,seip2022,fuzzing22,MindGap,ContextPMT,FSE24UM}
thus far and a major software release. {\bf
  Broader
  Impact:}  Work from this project has already
resulted in the reporting and correction of mulitple bugs in software
systems, including widely used production compilers.

{\paragraph{Co-PI Nghiem} is a co-PI on the Distributed Sensing \& Computing Over Sparse Environments (DISCOVER) Platform funded by an NSF CCRI grant (2120485), with a total budget of \$1,366,513 from 10/2021 until 9/2025.  {\bf Intellectual Merit:} DISCOVER is a cyberinfrastructure testbed for remote, rural, and sparsely populated areas, consisting of a fabric of highly configurable fixed and mobile sensor nodes and a heterogeneous wireless network.  It will enable focused research on new breeds of algorithms that address a range of challenges around prioritization and optimization of computation and communication in remote, less populous and rural areas.  {\bf Broader Impact:} DISCOVER will provide a research platform for investigation of distributed computing, networking, security, control and coordination solutions in a heterogeneous configurable cyber-physical system infrastructure that will provide critical services for areas and populations at increasing risk of being underserved. The education and outreach impacts of this project include training and research opportunities for undergraduate students, engaging underrepresented minority students, and developing hands-on research experiments for K-12 students.

% Flikkema is co-PI on the Southwest Experimental Garden Array (SEGA)
% funded by an NSF development MRI
% (DEB-1126840), with a total budget of \$2,848,876 from 10/2011 until
% 9/2017. {\bf Intellectual Merit:} SEGA is a facility
% distributed across a 1615m elevation gradient in Arizona that supports
% long-term research to increase understanding of and mitigate climate
% change using knowledge of genetic variation in species of concern. It
% consists an array of eleven gardens and supporting distributed
% monitoring and control cyberinfrastructure for the study of
% gene-by-environment interactions and enabling development of
% strategies to best manage for future climates. {\bf Broader
%   Impact:}  With 9 successfully completed projects to date, SEGA
% currently supports 11 experiments and has resulted in over 35
% publications and 20 conference presentations.  SEGA results are
% available online~\cite{SEGA}.


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
