\section{Related Work}

A fundamental goal of this project is to reduce both user effort and
the opportunity for user effort by allowing minimizing (ideally to
one) the number of times a user must specify an aspect of system
correctness.  The principle that important information should have a
``single point of truth'' is widely accepted in software engineering,
even in such foundational early advances as avoiding repeated magic
numbers by the use of named constants.  Such a principle can be
extended to specification and definition of test harnesses.  Early
work emphasizing this goal of both reducing work and chance of error
in specification and test generation included the effort by Groce and
Joshi to use a single harness for both model-checking and random
testing, in the verification of the Mars Science Laboratory's file
system \cite{WODA08,CFV08,AMAI}.  In later work, Groce and Erwig
extended this idea to propose development of a single language with a
unified semantics for a wide variety of dynamic test generation tools
\cite{WODACommon}; this approach is essentially realized in the
DeepState \cite{DeepState} system.  Indeed, \framac and
\acsl~\cite{ACSL} and DeepState are both arguably limited
instantiations of this goal: providing a single language, interface,
and semantics that is applied to a variety of methods (static or
dynamic) for checking that a specification holds.  This project aims
to further extend this goal by extending it to include a formal
timed-automata model and to connect the primarily static and dynamic approaches.

The implementation and verification of distributed systems,
and code extraction from automata modeling in the proof assistant
\Coq~\cite{WWP2015:PLDI,WWA2016:CPP,DBLP:conf/tacs/Paulin-Mohring01}
is a topic of some previous work.  Such  proposals require that the developers master \Coq, and start from the modeling activity to generate code.
They are therefore not applicable in the context of the verification
of legacy embedded C code, the common case in the real world.

Testing real-time systems modeled by networks of timed automata was
investigated by the authors of the tool \uppaal
\cite{uppaaltron2008,uppaalcover2007,uppaaltron2005} and implemented
in the tools \uppaal-TRON
and
\uppaal-COVER. These tools generate
tests, either offline or online, for conformance testing of a
real-time system with respect to its model and an environment model,
both as timed automaton networks.  In both cases, the real-time system
is considered a black-box with an input/output interface through which
the test generator or monitor can change the system inputs and observe
the system outputs.  The actual implementation code is not considered
and is in fact hidden from the testing tools.  While this approach is
general, it has several drawbacks.  It requires a centralized
input/output interface accessible to the testing tools.  Such an
interface is not always available in all systems, especially in
large-scale distributed systems like the sensor/actuator networks
considered in our case study.  Furthermore, by considering only the
(timed) input/output behavior of a system, this approach may not be
able to test internal system behaviors and therefore miss
opportunities for a better test
coverage.



% ;;; Local Variables: ***
% ;;; mode: latex ***
% ;;; eval: (ispell-change-dictionary "english" nil) ***
% ;;; eval: (flyspell-buffer) ***
% ;;; End: ***
