\documentclass[11pt]{article}
% -------------------------------------------------
\usepackage{fontspec}
\setmainfont{Times New Roman}
\usepackage[in]{fullpage}
\usepackage[utf8]{inputenc}
\usepackage[numbers]{natbib}
\usepackage{doi}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{footnote}
\makesavenoteenv{tabular}
% -------------------------------------------------
\begin{document}

\noindent{\large \bf Frédéric \textsc{Loulergue}}

\paragraph{(a) Professional Preparation} ~

~

\begin{tabular}{lllll}
Université d'Orléans& Orléans, France& Mathematics     & BSc& 1995 \\[3pt]
Université d'Orléans& Orléans, France& Computer Science& MSc& 1996 \\[3pt]
Université d'Orléans& Orléans, France& Computer Science& PhD& 2000 \\[3pt]
Université Paris-Est Créteil& Créteil, France& Computer Science& HDR\footnote{Habilitation à diriger
                                                                                                                                                 des recherches} & 2004
\end{tabular} 

% A list of the individual’s undergraduate and graduate education and postdoctoral training (including location) as indicated below:

% Undergraduate Institution(s)     Location    Major    Degree & Year

% Graduate Institution(s)          Location    Major    Degree & Year

% Postdoctoral Institution(s)      Location    Area     Inclusive Dates (years)

\paragraph{(b) Appointments} ~

~
% A list, in reverse chronological order, of all the individual's academic/professional appointments beginning with the current appointment.

\begin{tabular}{llll}
  Northern Arizona University & Flagstaff, AZ, USA    & Professor            & Aug 2016 -- now      \\[3pt]
  Université d'Orléans        & Orléans, France       & Professeur           & Sep 2013 -- Aug 2016 \\
                              &                       & 1$^\text{re}$ classe\footnote{Equivalent to Full Professor}\\[3pt]
  Inria, team $\pi r^2$       & Paris, France         & Visiting             & Sep 2014 -- Aug 2015 \\
                              &                       & Researcher           &                      \\[3pt]
  Université d'Orléans        & Orléans, France       & Professeur & Sep 2005 -- Aug 2013 \\
                              &                       & 2$^\text{nd}$ classe\footnote{Equivalent to Associate Professor}&                      \\[3pt]
  The University of Tokyo     & Tokyo, Japan          & JSPS Fellow          & Jul 2007 -- Aug 2007 \\[3pt]
  Université Paris-Est Créteil& Créteil, France       & Maître de\footnote{Equivalent to Assistant Professor}  & Sep 2000 -- Aug 2005 \\
                              &                       &  conférences \\[3pt]             
  Université d'Orléans        & Orléans, France       & Lecturer             & Sep 1999 -- Aug 2000
\end{tabular}


\paragraph{(c) Products} ~

~


\noindent{\it (i) Products related to the Proposed Project}

%\nocite{BKL2018:NFM,LBK2018:TAP,BLK2017:VPT,BKL2016:SCAM,BKL2015:FMICS}


\begin{enumerate}
\providecommand{\natexlab}[1]{#1}
\providecommand{\url}[1]{\texttt{#1}}
\expandafter\ifx\csname urlstyle\endcsname\relax
  \providecommand{\doi}[1]{doi: #1}\else
  \providecommand{\doi}{doi: \begingroup \urlstyle{rm}\Url}\fi

\item Allan Blanchard, Nikolai Kosmatov, and Fr\'{e}d\'{e}ric
  Loulergue.  \newblock {Ghosts for Lists: A Critical Module of
    Contiki Verified in Frama-C}.  \newblock In \emph{Nasa Formal
    Methods}, number 10811 in LNCS, pages 37--53.  Springer, 2018.
  \newblock \doi{10.1007/978-3-319-77935-5_3}.

\item Fr\'{e}d\'{e}ric Loulergue, Allan Blanchard, and Nikolai
  Kosmatov.  \newblock Ghosts for lists: from axiomatic to executable
  specifications.  \newblock In \emph{Tests and Proofs (TAP)}, volume
  10889 of \emph{LNCS}, pages 177--184. Springer, 2018.  \newblock
  \doi{10.1007/978-3-319-92994-1_11}.

\item Allan Blanchard, Fr\'ed\'eric Loulergue, and Nikolai Kosmatov.
  \newblock {From Concurrent Programs to Simulating Sequential
    Programs: Correctness of a Transformation}.  \newblock In Alexei
  Lisitsa, Andrei~P. Nemytykh, and Maurizio Proietti, editors,
  \emph{Proceedings Fifth International Workshop on Verification and
    Program Transformation, Uppsala, Sweden, 29th April 2017}, volume
  253 of \emph{Electronic Proceedings in Theoretical Computer
    Science}, pages 109--123. Open Publishing Association, 2017.
  \newblock \doi{10.4204/EPTCS.253.9}.

\item Allan Blanchard, Nikolai Kosmatov, Matthieu Lemerre, and
  Fr\'{e}d\'{e}ric Loulergue.  \newblock conc2seq: A {F}rama-{C}
  plugin for verification of parallel compositions of {C} programs.
  \newblock In \emph{16th IEEE International Working Conference on
    Source Code Analysis and Manipulation (SCAM)}, pages 67--72,
  Raleigh, NC, USA, 2016.  IEEE.  \newblock
  \doi{10.1109/SCAM.2016.18}.

\item Allan Blanchard, Nikolai Kosmatov, Matthieu Lemerre, and
  Fr\'{e}d\'{e}ric Loulergue.  \newblock A case study on formal
  verification of the {A}naxagoros hypervisor paging system with
  {F}rama-{C}.  \newblock In \emph{International Workshop on Formal
    Methods for Industrial Critical Systems (FMICS)}, LNCS, pages
  15--30, Oslo, Norway, June 2015.  Springer.  \newblock
  \doi{10.1007/978-3-319-19458-5_2}.

\end{enumerate}

\noindent{\it (ii) Other Significant Products} ~

\begin{enumerate}
  
  \providecommand{\natexlab}[1]{#1}
  \providecommand{\url}[1]{\texttt{#1}}
  \expandafter\ifx\csname urlstyle\endcsname\relax
  \providecommand{\doi}[1]{doi: #1}\else
  \providecommand{\doi}{doi: \begingroup \urlstyle{rm}\Url}\fi

\item Allan Blanchard, Nikolai Kosmatov, and Fr\'{e}d\'{e}ric
  Loulergue.  \newblock {MMFilter}: A {CHR}-based solver for
  generation of executions under weak memory models.  \newblock
  \emph{Comput Lang Syst Str}, 53:\penalty0 121--142, 2018.  \newblock
  \doi{10.1016/j.cl.2018.03.002}.


\item Fr\'{e}d\'{e}ric Loulergue, Wadoud Bousdira, and Julien Tesson.
  \newblock {Calculating Parallel Programs in Coq using List
    Homomorphisms}.  \newblock \emph{Int J Parallel Prog}, 2017.
  \newblock \doi{10.1007/s10766-016-0415-8}.

\item Fr\'ed\'eric Dabrowski, Fr\'ed\'eric Loulergue, and Thomas
  Pinsard.  \newblock A formal semantics of nested atomic sections
  with thread escape.
  \newblock \emph{Comput Lang Syst Str}, 42:\penalty0 2--21, 2015.\\
  \newblock \doi{10.1016/j.cl.2015.04.001}.
  
\item Kento Emoto, Fr\'{e}d\'{e}ric Loulergue, and Julien Tesson.
  \newblock {A Verified Generate-Test-Aggregate Coq Library for
    Parallel Programs Extraction}.  \newblock In \emph{Interactive
    Theorem Proving (ITP)}, number 8558 in LNCS, pages 258--274, Wien,
  Austria, 2014. Springer.  \newblock
  \doi{10.1007/978-3-319-08970-6_17}.

\item Fr\'ed\'eric Loulergue, Simon Robillard, Julien Tesson, Joeffrey
  L\'{e}gaux, and Zhenjiang Hu.  \newblock {Formal Derivation and
    Extraction of a Parallel Program for the All Nearest Smaller
    Values Problem}.  \newblock In \emph{ACM Symposium on Applied
    Computing (SAC)}, pages 1577--1584, Gyeongju, Korea, 2014. ACM.
  \newblock \doi{10.1145/2554850.2554912}.

    
\end{enumerate}

% A list of: (i) up to five products most closely related to the
% proposed project; and (ii) up to five other significant products,
% whether or not related to the proposed project. Acceptable products
% must be citable and accessible including but not limited to
% publications, data sets, software, patents, and
% copyrights. Unacceptable products are unpublished documents not yet
% submitted for publication, invited lectures, and additional lists of
% products. Only the list of ten will be used in the review of the
% proposal.

% Each product must include full citation information including (where
% applicable and practicable) names of all authors, date of publication
% or release, title, title of enclosing work such as journal or book,
% volume, issue, pages, website and URL or other Persistent Identifier.

% If only publications are included, the heading "Publications" may be
% used for this section of the Biographical Sketch.

\paragraph{(d) Synergistic Activities}

% A list of up to five examples that demonstrate the broader impact of
% the individual’s professional and scholarly activities that focuses on
% the integration and transfer of knowledge as well as its
% creation. Examples could include, among others: innovations in
% teaching and training (e.g., development of curricular materials and
% pedagogical methods); contributions to the science of learning;
% development and/or refinement of research tools; computation
% methodologies, and algorithms for problem-solving; development of
% databases to support research and education; broadening the
% participation of groups underrepresented in STEM; and service to the
% scientific and engineering community outside of the individual’s
% immediate organization.

\begin{enumerate}
\item Tutorials about Frama-C applied to the verification of the
  Contiki OS at ZINC'18, HPCS'18, IEEE SecDev'18, IEEE ISSRE'18;
  tutorials about Certified Parallel Program Calculation in Coq at
  IEEE HPCS'17, ACM SAC'16, and IEEE HPCS'14. For all tutorials,
  virtual machine images containing the necessary tools were provided.
\item Course CS451/551 ``Mechanized Reasoning about Programs'' at
  Northern Arizona University.
\item Co-chairs of Formal Approaches to Parallel and Distributed
  Systems (4PAD) affiliated to Euromicro PDP (2016) and HPCS (2018).
  Managing guest co-editor of a 4PAD special issue of the Journal of
  Logical and Algebraic Methods in Programming.
\item Member of the editorial boards of
  \href{http://www.scpe.org}{Scalable Computing: Practice and
    Experience}. Guest editor and co-editor of special issues of
  Future Generation Computer Systems, Scalable Computing: Practice and
  Experience, Parallel Processing Letters, Computer Languages Systems
  and Structures, International Journal of Parallel Programming.
\item Steering Committee Member of the High Level Parallel Programming
  Symposia since 2013.
\end{enumerate}


% ;;; Local Variables: ***
% ;;; eval: (ispell-change-dictionary "english" nil) ***
% ;;; mode: latex ***
% ;;; eval: (flyspell-buffer) ***
% ;;; End: ***

%\bibliography{bibliography}
%\bibliographystyle{unsrtnat}

\end{document}
